### 2018-08-08 paper/spor.tex
introduced theta

\((d, \pk_d, \avail_d)\gets \GetRandomNode\): We assume that there is an 
algorithm \(\GetRandomNode\) which returns a tuple \((d, \pk_d, \avail_d)\) of 
one uniformly randomly selected node, where.
\begin{itemize}
  \item \(d\) is the node's identifier (address);
  \item \(\pk_d\) is the node's public key;
  \item \(\avail_d(t)\) is the node's probability of being online as a function 
    of time.
\end{itemize}
The \(\GetRandomNode\) algorithm can be instantiated using \eg
Octopus~\cite{Octopus}. Its function is analogous to 
Tor's authoritative directory servers, but we need a decentralized system. 
We will treat \(\avail_d\) in \cref{sec:squad_overlay}.

@@

>>>>

\((d, \pk_d, \avail_d)\gets \GetRandomNode\): We assume that there is an 
algorithm \(\GetRandomNode\) which returns a tuple \((d, \pk_d, \avail_d)\) of 
one uniformly randomly selected node, where.
\begin{itemize}
  \item \(d\) is the node's identifier (address);
  \item \(\pk_d\) is the node's public key;
  \item \(\avail_d\) is the node's probability of being online in the near future. It computation will be discussed in~\ref{ssec:device_availability}.
\end{itemize}
The \(\GetRandomNode\) algorithm can be instantiated using \eg
Octopus~\cite{Octopus}. Its function is analogous to 
Tor's authoritative directory servers, but we need a decentralized system. 
We will treat \(\avail_d\) in \cref{sec:squad_overlay}.

@@

For the evaluaion of the impact of devices' availability prediction, we introduce a parameter, coined the \emph{availability threshold} $\theta$. 
\CreateLayer iteratively adds nodes to a layer \layer until its probability of being entirely offline $\Poff^\layer$ falls below $\theta$ or $w_\layer$ is reached:

$$ \Poff^\layer = \sum\limits_{d \in \layer}(1 - \desc_d.\Pon_d) $$

When $|\layer| < w_\layer$, the layer is filled with empty descriptors so as to fill the target number of nodes per layer.

Using $\theta$, \name becomes more conservative than \SPOR, and we can investigate the best number of nodes per layer in regard of its probability of being available.
